MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-17 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
test phase III

#### Phase I (clinical, ancestry and sample specific technical variables)
```{r phase1}
# Fit a base model with the following covariates
base_covars <- "Dx.Tissue"
random_effect <- "Individual_ID"

# Set base formula
base_formula <- glue::glue("~ ", glue::glue_collapse(base_covars, sep = " + ")) %>% 
  glue::glue(" + (1|{random_effect})")

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = base_formula, 
                         data = COVARIATES,
                         variables = array(c("(1|Institution)", "(1|Reported_Gender)", "PMI", 
                                                             "ageOfDeath", "RIN", "RIN2", "EV.1", 
                                                             "EV.2", "EV.3", "EV.4", "EV.5")))
phase1
```

#### Phase II (batch effects)
```{r phase2}
phase2 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = phase1$formula, 
                         data = COVARIATES,
                         variables = array(c("(1|LibraryBatch)", "(1|FlowcellBatch)")))
phase2
```

#### Phase III (RNASeq alignment specific covariates)
```{r phase3}
phase3 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = phase2$formula, 
                         data = COVARIATES,
                         variables = array(c("IntragenicRate", "IntronicRate","IntergenicRate","rRNARate", "(1|TotalReads)", "GenesDetected", "MappedReads")))
phase3
```

>>>>

<!-- #### Phase I (clinical, ancestry and sample specific technical variables) -->
<!-- ```{r phase1} -->
<!-- # Fit a base model with the following covariates -->
<!-- base_covars <- "Dx.Tissue" -->
<!-- random_effect <- "Individual_ID" -->

<!-- # Set base formula -->
<!-- base_formula <- glue::glue("~ ", glue::glue_collapse(base_covars, sep = " + ")) %>%  -->
<!--   glue::glue(" + (1|{random_effect})") -->

<!-- # Stepwise regression -->
<!-- phase1 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN, -->
<!--                          baseFormula = base_formula,  -->
<!--                          data = COVARIATES, -->
<!--                          variables = array(c("(1|Institution)", "(1|Reported_Gender)", "PMI",  -->
<!--                                                              "ageOfDeath", "RIN", "RIN2", "EV.1",  -->
<!--                                                              "EV.2", "EV.3", "EV.4", "EV.5"))) -->
<!-- phase1 -->
<!-- ``` -->

<!-- #### Phase II (batch effects) -->
<!-- ```{r phase2} -->
<!-- phase2 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN, -->
<!--                          baseFormula = phase1$formula,  -->
<!--                          data = COVARIATES, -->
<!--                          variables = array(c("(1|LibraryBatch)", "(1|FlowcellBatch)"))) -->
<!-- phase2 -->
<!-- ``` -->

#### Phase III (RNASeq alignment specific covariates)
```{r phase3}
phase2_formula <- "~Dx.Tissue + (1 | Individual_ID) + RIN2 + (1 | Institution) + ageOfDeath + RIN + PMI + EV.1 + (1 | Reported_Gender) + EV.2 + EV.3 + EV.4"
phase3 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = phase2_formula, 
                         data = COVARIATES,
                         variables = array(c("IntragenicRate", "IntronicRate","IntergenicRate","rRNARate", "TotalReads", "GenesDetected", "MappedReads")))
phase3
```
